\documentclass{resume} % Use the custom resume.cls style

\usepackage[left=0.4 in,top=0.4in,right=0.4 in,bottom=0.4in]{geometry} % Document margins
\newcommand{\tab}[1]{\hspace{.2667\textwidth}\rlap{#1}} 
\newcommand{\itab}[1]{\hspace{0em}\rlap{#1}}
\name{Karen George\vspace{-8pt}} % Your name
%\address{123 Pleasant Lane \\ City, State 12345} % Your secondary addess (optional)
\address{k.george1@usa.edu \\ (408)-931-3943}  % Your phone number and email

\begin{document}
\vspace{-15pt}
%	EDUCATION
\begin{rSection}{Education}
{\bf University of St. Augustine for Health Sciences}, Doctor of Physical Therapy  \hfill {Expected Dec 2019}

{\bf University of California, Davis}, Bachelor of Science in Exercise Biology  \hfill {Sep 2015}
\end{rSection}
%   PT EXPERIENCE
\begin{rSection}{PHYSICAL THERAPY EXPERIENCE}
{\textbf{Granite Peak Physiotherapy, \textit{Outpatient \& Home Care,}} Stanthorpe, QLD AU
\hfill Sep 2019--Nov 2019 \\
Performed extensive manual therapy in the management of outpatient conditions including dysfunctions of the cervical, lumbar, hip, knee, ankle, shoulder, elbow, and hand regions. Managed older adult patients following stroke and post-operative joint replacements in home and outpatient setting. Presented an in-service on Heat Wrap Therapy for Acute Low Back Pain.
}
\\\\
{\textbf{Floyd Medical Center, \textit{Outpatient Orthopedic \& Sports,}} Rome, GA
\hfill May 2019--Aug 2019 \\
 Designed individualized therapeutic exercise and comprehensive rehabilitation for adult and youth patients with osteoarthritis, fractures, rotator cuff tear and impingement, lumbar and cervical pain, and post-surgical shoulder, knee and hip procedures. Incorporated use of Blood Flow Restriction, Instrument Assisted Soft Tissue Mobilization, and Electrical Stimulation Modalities. Presented an in-service on Post-Operative Rehabilitation Following Hip Labrum Repair.}
 \\\\
{\textbf{Northgate Postacute Care, \textit{Skilled Nursing Facility,}} San Rafael, CA
\hfill Sep 2018--Oct 2018 \\
 Evaluated and treated adult and geriatric patients with post-surgical joint replacement, stroke, Parkinson's Disease, contractures, and generalized weakness following prolonged hospitalization. Collaborated with a multidisciplinary team. Presented in-service on Sensory Deficits and Balance.}
 \\\\
 {\textbf{DS Physical Therapy \& Sportscare, \textit{Physical Therapy Aide,}} San Jose, CA
\hfill Oct 2015--Apr 2017 \\
 Outpatient orthopedic clinic. Participated in scheduling, billing, and training new aide employees.}
\end{rSection} 

%	RESEARCH
\begin{rSection}{RESEARCH}
{\textbf{University of St. Augustine, \textit{Research Assistant,}} San Marcos, CA \hfill Mar 2019--May 2019 \\
Normative Pelvic Floor Parameters in Adults Assessed Using Transabdominal Ultrasound. \\Primary Investigators: Iman Akef and Heather Disney}
\\\\
{\textbf{University of St. Augustine, \textit{Research Assistant,}} San Marcos, CA \hfill Mar 2019--May 2019 \\
17 Beta-Estradiol Induced Effects on Anterior Cruciate Ligament Laxity, Tendon Mechanical Properties \\and Endothelial Function in Females. Primary Investigators: Iman Akef and Lena Volland}
\end{rSection} 
%	TEACHING
\begin{rSection}{TEACHING}
{\textbf{University of St. Augustine, \textit{Teaching Assistant,}} San Marcos, CA \hfill Jan 2019--Apr 2019 \\
Taught first year Doctor of Physical Therapy students in Gross Anatomy Cadaver Laboratory.}
\\\\
{\textbf{University of St. Augustine, \textit{Tutor,}} San Marcos, CA \hfill Jan 2018--Dec 2018 \\
Mentored DPT students in Musculoskeletal, Gross/Applied Anatomy, \\Biomechanics, Neuromuscular, Movement Science, Cardiopulmonary, Biophysical Agents, and Spine.}
\end{rSection} 

%	CONTINUING EDUCATION
\begin{rSection}{CONTINUING EDUCATION}
{\textbf{Understanding Dementia}} \hfill July 2019\\
University of Tasmania \& Wicking Dementia Research \& Education Centre }
\end{rSection}

%	CAMPUS INVOLVEMENT
\begin{rSection}{CAMPUS INVOLVEMENT}
{\textbf{Student Newsletter, \textit{Writer}} \hfill{Jan 2018--Apr 2019}}
\\
{\textbf{Lunch \& Learn: Combined Sections Meeting \& Conference Experience, \textit{Presenter}} \hfill{Mar 2019}}
\end{rSection} 
%	PROFESSIONAL ORGANIZATIONS
\begin{rSection}{PROFESSIONAL ORGANIZATIONS}
{\textbf{California Physical Therapy Association (CPTA), \textit{Education Committee}} \hfill{Jan 2019--Dec 2019}}
\\
{\textbf{American Physical Therapy Association (APTA)}\\
\-\hspace{5mm} --- \textit{Academy of Geriatric Physical Therapy}
\-\hspace{5mm} --- \textit{Section on Research}}
\end{rSection} 
%	CONFERENCES
%\begin{rSection}{CONFERENCE ATTENDANCE}
%{\textbf{Combined Sections Meeting (CSM) 2019} \hfill{Jan 2019}}
\\
%{\textbf{California Physical Therapy Association (CPTA) Annual Conference 2018} \hfill{Sep 2018}}\\
%{\textbf{Combined Sections Meeting (CSM) 2018} \hfill{Feb 2018}}
\end{rSection}
\end{document}
